Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling

### 2022-10-14 MDPI/reviewer1.tex
proofreading

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
\usepackage{subfig}
\usepackage[textsize=small]{todonotes}
\newcommand{\ie}{\textit{i.~e.} }
\newcommand{\cref}{c^{\ominus}}
%\newcommand{\cs}{c_{s}}
\newcommand{\kT}{k_\mathrm{B}T}
\newcommand{\kB}{k_\mathrm{B}}
\newcommand{\lb}{l_\mathrm{B}}
%\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\NA}{N_{\mathrm{A}}}
\newcommand{\muna}{\mu_\mathrm{Na^+}}

@@

\newcommand{\gel}{^\mathrm{gel}}
\newcommand{\tot}{^\mathrm{tot}}
\newcommand{\out}{^{\mathrm{out}}}
\newcommand{\coh}{c_\mathrm{OH}}
\newcommand{\bulk}{^{\mathrm{b}}}
\renewcommand{\H}{\mathrm{H^+}}
\newcommand{\A}{\mathrm{A^-}}
\newcommand{\AH}{\mathrm{AH}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations

\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\na}{\mathrm{Na^+}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}

\newcommand{\Ka}{K_{\mathrm{A}}}
\newcommand{\pKa}{\mathrm{p}\Ka}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\mol}{\mathrm{mol}}
\newcommand{\molperl}{\mathrm{mol/l}}
\newcommand{\kg}{\mathrm{kg}}
\newcommand{\res}{^{\mathrm{res}}}
\newcommand{\pHres}{\pH\res}
\newcommand{\pHgel}{\pH\gel}
\newcommand{\cs}{c_{\mathrm{s}}}
%\newcommand{\cs}{c_{\mathrm{salt}}}
\newcommand{\csres}{\cs\res}
%\newcommand{\Vgel}{V\gel}
\newcommand{\Vgel}{V_\mathrm{gel}}
\newcommand{\vgel}{v_\mathrm{gel}}
\newcommand{\Egel}{E_\mathrm{gel}}
\newcommand{\Sgel}{S_\mathrm{gel}}
%\newcommand{\Vgel}{V}
\newcommand{\Ngel}{N_\mathrm{gel}}
%\newcommand{\Vgeleq}{\widetilde{V}_\mathrm{gel}}}
%\newcommand{\Pgel}{P_\mathrm{gel}}
\newcommand{\Pgel}{\Pi}
\newcommand{\Pres}{P_\mathrm{res}}
\newcommand{\Pout}{P_\mathrm{out}}
\newcommand{\Vout}{V_\mathrm{out}}
\newcommand{\Eout}{E_\mathrm{out}}
\newcommand{\Sout}{S_\mathrm{out}}
%\newcommand{\Vbox}{V_\mathrm{box}}
\newcommand{\Vbox}{V_0}
\newcommand{\PE}{polyelectrolyte{}}

\newcommand{\reffig}[1]{Figure~\ref{#1}}
\newcommand{\refeq}[1]{Equation~\ref{#1}{}}
\newcommand{\etal}{\textit{et al.}{}}

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0003-3412-7707} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0003-3616-3285} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-8501-0464} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Mikhail Laktionov $^{1, 2}$\orcidA{}, Lucie Nová $^{1}$\orcidB{} and Oleg V. Rud $^{1, 3}$*\orcidC{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Mikhail Laktionov, Lucie Nová and Oleg V. Rud}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Czech Republic; e-mail@e-mail.com\\
$^{2}$ \quad St. Petersburg National Research University of Information Technologies, Mechanics and Optics, St. Petersburg, Russia; e-mail@e-mail.com\\
$^{3}$ \quad Institute of Macromolecular Compounds of Russian Academy of Sciences, Saint-Petersburg, Russia; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: oleg.rud@natur.cuni.cz; }

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).
Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane rejecting ions between external and internal solutions.
These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.
In this article, we present our recent theoretical study of the use of polyelectrolyte hydrogel for water desalination. 
We modeled the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous salt solution.
We have shown that the salinity of the supernate phase decreases during compression of the gel due to the release of absorbed in gel solution of lower salinity. 
Finally, we performed a set of simulations modeling the process of continuous decrease of solution salinity up to freshwater concentrations.
}

% Keywords
\keyword{polyelectrolye hydrogel; simulation; desalination}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%
%	\begin{itemize}[labelsep=2.5mm]
%		\item This is an obligatory section in ``Advances in Respiratory Medicine'', whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
%		\item Highlights consist of a short collection of (3–6) bullet points that capture the gap in knowledge the manuscript is addressing, as well as breakthroughs and other important points.
%		\item The Highlights section may also be used to showcase a new method used during the study (if any).
%	\end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.

\section{Introduction\label{sec: intro}}
\subsection{Water desalination technologies.}
Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

The first approach is distillation, which uses heat to cause a phase change of the water to vapor. The vapor phase is separated from the brine and condenses to liquid fresh water. 
The released condensation energy is directed back to heating the feed solution.
Distillation processes were the first desalination techniques conducted on a large commercial scale and still account for a large portion of the modern world’s desalination capacity.

The second approach is to physically separate the brine components using an osmotic membrane transparent only for water molecules, which move in response to a water chemical potential difference.
In the context of our study, we will mention the reverse osmosis process (RO)~--- the major process of all the modern desalination industry, and the newly emerging membrane
technology~--- forward osmosis (FO) \cite{Akther2015}. 
In RO, the difference in water chemical potential originates from a difference in pressures applied to the feed and to product solutions. 
In FO, the chemical potential difference is due to an addition to solution from one side of the membrane (draw solution) the so-called draw solutes, which are lowering the water chemical potential in draw solution.

Distillation is easy and cheap technology but it is characterized by relatively high energy costs due to the dissipation of thermal energy. 
On the contrary, RO uses expensive osmotic membranes, which need to be replaced regularly because of scaling and fouling. 
Moreover, RO requires very high operating pressures, ranging from 20 to 200 bar, to let the water pass through the membrane. 
But in terms of energy losses, it works close to the thermodynamic limit.
Thus, theoretically, per one ion pair transferred from freshwater to salty water, it consumes only the energy equal to the difference between the chemical potentials of the transfered ions.

The absence of large hydraulic pressure in FO process (unlike in RO) allows to reduce the energy consumption in pumping, reduce membrane scaling and fouling, and therefore significantly increase the lifetime of the membranes. 
In FO, the draw solutes (agents) are dispersed and/or dissolved in water form homogeneous draw solutions. 
The correct choice of the draw agents is a task of paramount importance. 
As an osmotically driven process, the draw solute is expected to significantly reduce the water chemical potential, and consequently generate a high osmotic pressure. 
On the other hand, the draw solute is expected to be easily separated from water \cite{Cai2016}.

\subsection{Hydrogels for desalination.}
Hydrogels are three-dimensional networks of polymer chains that are crosslinked by either physical or chemical bonds. 
They are able to entrap large volumes of water attracted by the high concentration of hydrophilic groups. 
When a dehydrated or deswollen hydrogel uptakes water, its polymer chains extend, creating a swelling pressure. 
For example, as reported in \cite{Wack_2009} weakly crosslinked poly(acrylic acid) (PAA) copolymers with polymer volume fractions between 0.03 and 0.30 exhibit a swelling pressure ranging from 0.20--4.23 MPa.
Polyelectrolyte hydrogels, which are carrying ionic groups on the comonomer units (like PAA), are able to reject salt ions from the solution, they absorb a solution of lower salinity than that they are equilibrated with.

An important, advantageous aspect of polymer hydrogels is that they can undergo reversible volume change, \ie solution --- gel phase transitions in response to environmental stimuli. 
This aspect causes hydrogels to be labeled as ‘smart’ hydrogels. 
Many physical and chemical stimuli have been applied to induce various responses of such smart hydrogels, in particular, to change them from hydrophilic to hydrophobic, thereby releasing water. 
The physical stimuli include: temperature, solvent composition, light, mechanical pressure, sound, electric and/or magnetic field, whilst the chemical (or biochemical) stimuli include pH, ionic strength, and specific molecular recognition \cite{Tanaka_1982,Serizawa_2001,Lietor_Santos_2009,Qiu_2001}.

The smart properties of hydrogels were utilized for desalination in a recent study by Li \etal \cite{Li2011}, where hydrogels have been considered as draw agents for FO. 
In this study authors have shown, that hydrogels, 
are able to absorb water across the FO membrane due to their swelling and osmotic pressure and
allow dewatering under the influence of stimuli (thermal and/or mechanical), due to their insoluble cross-linked polymer network.
For instance, Li \etal proposed the use of hydrogel made of thermoresponsive polyelectrolyte~--- copolymer of poly-N-isopropyl acrylamide (p-NIPAAm) and polyacrylic acid (p-AA).
Depending on the temperature the network of the gel appears to be either hydrophilic or hydrophobic. 
In the hydrophilic state, the gel is used as a draw solute accumulating water inside, then in the hydrophobic state, the water releases out.

Moreover, from a thermodynamics perspective, the polyelectrolyte hydrogel itself is an osmotic membrane generating Donnan potential, which rejects ions between outer and inner solutions \cite{Wang_2014}. 
Such a view on hydrogels was employed in a series of works by the group of prof. Wilhelm (see for example \cite{Arens_2017,Fengler_2020}). 
The authors of these works proposed to get rid of the osmotic membrane and simply use only micro filtration to compress the hydrogel squeezing out the accumulated inside the gel solution. 
In their method first, the deswollen hydrogel was equilibrated with saline water feed. 
During equilibration, the gel was swelling absorbing water. 
Then it was taken out from the feed solution and mechanically squeezed by means of a microfiltration membrane. 
The squeezed out brine was obtained to have lower salinity than the feed water.

A similar approach was used by Ali \etal \cite{Ali2015}. 
In their study the thermosensitive gel was used (based on copolymers p-NIPAAm and p-AA), so instead of physical compression, the dewatering was done by an external heating stimulus (sunlight). 
At night the gel was equilibrating with feed water and at daytime, under sunlight, the gel was shrinking and releasing the collected inside solution.

\subsection{Physics behind the desalination process.}
%The maximum entropy principle requires the density of charges to be more-less the same throughout the system medium. 
Since the polyelectrolyte gel has its own charges and its own neutralizing counterions, the density of mobile ions (which are able to freely enter and leave the gel) in gel appears to be smaller than their density outside the gel.
Therefore the internal solution of the gel has a lower density of mobile ions than that in the solution outside. 
In that sense, the gel acts as an osmotic membrane separating solutions \cite{Rud2020}. 
The driving force of the separation is the Donnan potential originated from the charges of the hydrogel network. 
The density of mobile ions difference between ions concentrations in the internal and external solutions
is defined by Donnan law \cite{Rud2018}
\begin{equation*}
\frac{\ccl\gel}{\cs}=\frac{\cs}{\cna\gel}=\sqrt{1+\left(\frac{\alpha}{2\cs\Vgel}\right)^{2}}\pm\frac{\alpha}{2\cs\Vgel}
\end{equation*}
where $\ccl\gel$ and $\cna\gel$ are the internal concentration of monovalent anions and cations, $\cs$ is the salinity of external solution,  $\Vgel$ is the gel molar volume (inverse density of gel segments) and $\alpha$ is ionization degree (in the case of our study $\alpha=1$). 
The $\pm$ sign in the formula accounts for the change between the cases of gel made of polyanion or polycation.

The lower salinity solution can be extracted from the gel by means of compression and/or other stimulus providing that the charge of the gel remains constant.
In the case of gel made of weak (pH-sensitive) polyelectrolyte, the compression discharges the gel, therefore the neutralizing counterions leave out the gel diminishing the desalination effect \cite{Rud2018}. 
%Nevertheless, in\cite{Rud2018} we discussed how the release of counterions may be employed for desalination as well.

One can argue that the sole Donnan effect is insufficient to achieve a high salt rejection \cite{Cai2016} and the salinity of the water squeezed from hydrogel under a very high hydraulic pressure (up to 100 bar \cite{Fengler_2020}) turns out to be not much different from the initial.
Indeed, the use of high hydraulic pressure diminishes all the advantages of this method over RO, and the reversibility of hydrogel swelling after strong compression remains questionable. 
Nevertheless, in the current study, we model the compression of the gel limiting ourselves to low compression rates, less than 5 bar, and studied how the compression of the gel affects the surrounding salinity.
We modelled also the desalination process, as a cascade of following one by each other gel swellings and compressions driving the salinity of supernate down to drinkable water. 
%In the current study we would like to concentrate on the use of gel made of strong polyelectrolyte for water desalination. 
%Namely, to investigate how the compression of the gel affects the salinity of the surrounding the gel solution and to propose the way of water desalination employing the hydrogel swelling/deswelling set of processes.

%The target of our study is to model the thermodynamic equilibrium between the two boxes and to show how the compression of the gel affects the ion density in the outside solution.

\section{Theory behind the simulation\label{sec: theory}}

\begin{figure*}[h]
\centering 
\includegraphics[width=0.7\textwidth]{{figures/simgibbs}.pdf}\caption{Diamond-like network in the simulation box. Color code represents
the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
($\A$)). \label{fig:diamond}.}
\end{figure*}

\subsection{Model}

We model the gel as a network of 16 linear polymer chains, each by 30 monomer units. 
The chains are connected to a diamond-like polymer network throught 8 crosslinking units, and put into a simulation box with periodic boundaries (see \reffig{fig:diamond}). 
Each unit of the network carries a negative electric charge, which is equal to the charge of electron. 
Except the particles of the network, the monovalent co- and counter-ions ions, $\cl$ and $\na$, are present in simulation box. 
The total electric charge of all the particles in the box is zero, therefore the amount of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units, $\Ngel=16\cdot30 + 8=488$.

We simulate the compression of the gel in two ensembles.
\begin{enumerate}
\item The first is so called \emph{open system}, when the simulation box with gel freely exchanges ions with a big amount of aqueous solution of certain constant salinity, $\cs$. 
\item The second is \emph{closed system}, when the gel is in equilibrium with a finite volume of aqueous solution.
\end{enumerate}
The compression of the gel in the \emph{open} system does not affect the surrounding salinity, thus the density of ions outside the gel remains constant $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
On the contrary, what remains constant in the \emph{closed} system, is the total number of $\na$ and $\cl$ ions, that are contained in the gel and in the external volume, \ie in the volume $\Vbox$ (\reffig{fig: closed}).

%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
\begin{equation}
N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
\end{equation}
where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. 
As $\Vbox$ we choose the volume of the gel in the free swelling equilibrium state.

%Then in closed system $\nna$ and $\ncl$ remain constant, whereas the salinity of supernate, $\cs$, may change with the change of the gel volume.

\begin{figure*}[h]
\centering 
\subfloat[Open system \label{fig: open}]
{\includegraphics[width=0.5\textwidth]{figures/gc.pdf}}
\subfloat[Closed system \label{fig: closed}]
{\includegraphics[width=0.5\textwidth]{figures/gibbs.pdf}}
\caption{Diamond-like network in the simulation box. Color code represents
the individual ion types (red: $\na$, blue: $\cl$, yellow: $\ca$)
and the hydrogel (gray: neutral segment ($\AH$), cyan: charged segment
($\A$)). \label{fig:open and closed}.}
\end{figure*}
\subsection{Open system.}
We simulate the open system using the grand reaction method \cite{Landsgesel2020a,Rud2020}.
This method is a hybrid of molecular dynamics (MD) and Monte Carlo (MC). 
The whole simulation represents a chain of subsimulations of MD and MC followed one by each other. 
For MD simulation we used a standard Langevin dynamics \cite{Grest1986} which models the mechanical movement of all the system particles. 
Whereas MC simulates the thermodynamic equilibrium with reservoir, which exchanges ions with the simulation box. 
The insertion (and deletion) of ion pairs is considered as a reaction of creation (or annihilation) of an ion pair 
\[
\varnothing\stackrel{K}{\leftrightarrows}\na+\cl
\]
with a reaction constant defined by the chemical potential of ions,
$K=\exp\left(\muna+\mucl\right).$

\subsection{Closed system.}
The similar scheme we use to simulate the gel in closed system. 
The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
These two boxes are represented in \reffig{fig:diamond}.

>>>>

\documentclass[12pt]{dinbrief}
%\usepackage{english}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[textsize=small]{todonotes}

\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=false, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=true] {hyperref}

%\usepackage[pdfborder={0 0 0}]{hyperref}

\date{\today}

\place{Prague}

\nowindowtics
\nowindowrules

\newcommand{\theeditor}{Dr. David Díaz-Díaz}

\newcommand{\thejournal}{\textit{Gels }}
\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\na}{\mathrm{Na^+}}

%\newcommand{\ie}{\textit{i.~e.} } 
\enabledraftstandard
\newcommand{\ie}{\textit{i.~e.} }
\newcommand{\cref}{c^{\ominus}}
%\newcommand{\cs}{c_{s}}
\newcommand{\kT}{k_\mathrm{B}T}
\newcommand{\kB}{k_\mathrm{B}}
\newcommand{\lb}{l_\mathrm{B}}
%\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\NA}{N_{\mathrm{A}}}
\newcommand{\muna}{\mu_\mathrm{Na^+}}

@@

\newcommand{\gel}{^\mathrm{gel}}
\newcommand{\tot}{^\mathrm{tot}}
\newcommand{\out}{^{\mathrm{out}}}
\newcommand{\coh}{c_\mathrm{OH}}
\newcommand{\bulk}{^{\mathrm{b}}}
\renewcommand{\H}{\mathrm{H^+}}
\newcommand{\A}{\mathrm{A^-}}
\newcommand{\AH}{\mathrm{AH}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}
\newcommand{\todoi}[1]{\todo[inline]{#1}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}
\newcommand{\so}{\mathrm{SO_4^{2-}}}

\newcommand{\EI}{E_{\mathrm{I}}}
\newcommand{\EII}{E_{\mathrm{II}}}
\newcommand{\SI}{S_{\mathrm{I}}}
\newcommand{\SII}{S_{\mathrm{II}}}
\newcommand{\NI}{N_{\mathrm{I}}}
\newcommand{\NII}{N_{\mathrm{II}}}
\newcommand{\VI}{V_{\mathrm{I}}}
\newcommand{\VII}{V_{\mathrm{II}}}
\newcommand{\FI}{F_{\mathrm{I}}}
\newcommand{\FII}{F_{\mathrm{II}}}
\newcommand{\nnaI}{N^{\na}_{\mathrm{I}}}
\newcommand{\nclI}{N^{\cl}_{\mathrm{I}}}
\newcommand{\nnaII}{N^{\na}_{\mathrm{II}}}
\newcommand{\nclII}{N^{\cl}_{\mathrm{II}}}

\newcommand{\Ka}{K_{\mathrm{A}}}
\newcommand{\pKa}{\mathrm{p}\Ka}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\mol}{\mathrm{mol}}
\newcommand{\molperl}{\mathrm{mol/l}}
\newcommand{\kg}{\mathrm{kg}}
\newcommand{\res}{^{\mathrm{res}}}
\newcommand{\pHres}{\pH\res}
\newcommand{\pHgel}{\pH\gel}
\newcommand{\cs}{c_{\mathrm{s}}}
\newcommand{\csres}{\cs\res}
\newcommand{\Vgel}{V_\mathrm{gel}}
\newcommand{\Ngel}{N_\mathrm{gel}}
\newcommand{\Pgel}{\Pi}
\newcommand{\Pres}{P_\mathrm{res}}
\newcommand{\Pout}{P_\mathrm{out}}
\newcommand{\Vout}{V_\mathrm{out}}
\newcommand{\Vbox}{V_0}
\newcommand{\PE}{polyelectrolyte{}}

\begin{document}

\textbf{Reviewer 1}
\textit{}

\begin{enumerate}
\item \textit{The main findings of your results should be highlighted in abstract}

We have rewritten the abstract.

\item \textit{Please do not separate introduction in three sections combine with problem and technology you used and challenges and your solutions.}

We have rewritten the Introduction section.
We wanted to keep the separation of the Introduction section into the respective subsections because the Introduction is relatively lengthy, so we believe that dividing it into subsections reduces its readability.

\item \textit{In page 4 heading 2. (How to start with and ??)}.\\
Corrected.

\item \textit{All formula and models should be supported with reference for instant equation 3.}
Corrected

\item \textit{In page 6, please remove the footer, it is not a book to describe issues below}.\\
Corrected. Now this sentence appears in text (in brackets).

\item \textit{How do you think control factors in open system such as pressure and temperature}

In our simulation, we control the volume of the simulation box and measure the pressure using the virial theorem. The pressure value which is depicted in the Figures assumed to be a partial pressure of the gel, which is calculated as the difference between the pressure in the gel and the pressure calculated in a separate simulation box containing only ions (with no gel).
Temperature assumed to be constant and equal to 300 K, which is guaranteed by applying a Langevin thermostat.

\end{enumerate}

\bibliographystyle{unsrt}
\bibliography{lit/gibbs}
\end{document}
